### 2016-09-25 paper/introduction.tex
added some citations

Bidirectional programming is used heavily in practice.
Augeas~\cite{?}, a configuration editing system for linux, uses lens combinators
to provide editable views of configuration files.
Bixid~\cite{?} is a language developed for expressing bidirectional XML
transformations.
XSugar~\cite{?} is used to convert bidirectionally between XML and non-XML data,
and is used to convert between EpiDoc~\cite{?} and Leiden+~\cite{?} formats for
encoding ancient documents~\cite{?}.
Serializers and deserializers combine to make a bidirectional program, though
they are rarely written in a domain specific language for bidirectional
programming.

Lenses are popular because they typically come with strong guarantees
about the get-put (and put-get) round-trip behavior.  Such guarantees
help users guard against data corruption while reading and editing
high-value data sources.  These guarantees are often achieved through
the use of domain-specific languages with strong type systems that
guarantee invertability of lens programs~\cite{?,?,?}.  Unfortunately, such
lens languages are currently quite non-standard.  The
process of writing a lens is challenging, as a user must think
about data conversion in two directions at once --- an
unusual task for the everyday programmer.  As a consequence, 
for the casual user of lenses, learning the language, its type system and its
unorthodox programming style is time-consuming and, in the end,
a disincentive to adopting the technology, despite its advantages.

@@

Recently, researchers have developed a number of new algorithms for
type-directed synthesis~\cite{?,?,?}.  Many of those
algorithms~\cite{osera+:pldi15,frankle+:popl16,armando+:pldi16} are
directed in part by the syntax of types.  For instance, to find an
expression with type $A \rightarrow B$, such algorithms will assume
that the expression in question is a function with the form $\lambda
x{:}A. e$, and they will continue the search for an expression $e$
with type $B$ under the hypothesis that the parameter $x$ has type
$A$.  In the case of the simply-typed lambda calculus, such an
approach reduces the complexity of the search for terms inhabiting the
type without losing completeness.  Lenses are defined by a richer type system
than the simply typed lambda calculus,
with their regular expression types, as
there are many equivalent ways to express the same regular expression.
Unfortunately, this makes simple
syntax-directed algorithms not directly applicable.

>>>>

Bidirectional programming is used heavily in practice.
Augeas~\cite{augeas}, a configuration editing system for linux, uses lens combinators
to provide editable views of configuration files.
The language biXid~\cite{bixid} is developed for expressing bidirectional XML
transformations.
XSugar~\cite{xsugar} is used to convert bidirectionally between XML and non-XML data,
and is used to convert between EpiDoc~\cite{epidoc} and Leiden+~\cite{leidenplus} formats for
encoding ancient documents~\cite{epidocleidenplus}.
Serializers and deserializers combine to make a bidirectional program, though
they are rarely written in a domain specific language for bidirectional
programming.

Lenses are popular because they typically come with strong guarantees
about the get-put (and put-get) round-trip behavior.  Such guarantees
help users guard against data corruption while reading and editing
high-value data sources.  These guarantees are often achieved through
the use of domain-specific languages with strong type systems that
guarantee invertability of lens programs~\cite{Focal2005-long,boomerang,symmetric-lenses}.  Unfortunately, such
lens languages are currently quite non-standard.  The
process of writing a lens is challenging, as a user must think
about data conversion in two directions at once --- an
unusual task for the everyday programmer.  As a consequence, 
for the casual user of lenses, learning the language, its type system and its
unorthodox programming style is time-consuming and, in the end,
a disincentive to adopting the technology, despite its advantages.

@@

Recently, researchers have developed a number of new algorithms for
synthesis~\cite{yag+:pldi16,?,?}.  Many of those
algorithms~\cite{osera+:pldi15,frankle+:popl16,armando+:pldi16} are
directed in part by the syntax of types.  For instance, to find an
expression with type $A \rightarrow B$, such algorithms will assume
that the expression in question is a function with the form $\lambda
x{:}A. e$, and they will continue the search for an expression $e$
with type $B$ under the hypothesis that the parameter $x$ has type
$A$.  In the case of the simply-typed lambda calculus, such an
approach reduces the complexity of the search for terms inhabiting the
type without losing completeness.  Lenses are defined by a richer type system
than the simply typed lambda calculus,
with their regular expression types, as
there are many equivalent ways to express the same regular expression.
Unfortunately, this makes simple
syntax-directed algorithms not directly applicable.
